Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828

### 2016-07-06 inst/examples/20160715-slides-Krakow.Rmd
ok

```{r language1-kungliga, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=8, out.width="150px", fig.show="hold"}
catalogue = "Kungliga"
  df <- dfl %>% filter(catalog == catalogue)
  df <- dfl %>% group_by(publication_decade, language) %>%
             summarise(n = n(),
	               paper = sum(paper.consumption.km2, na.rm = TRUE))

>>>>

```{r language1-kungliga, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=8, out.width="150px", fig.show="hold"}
catalogue = "Kungliga"
  df <- dfl %>% filter(catalog == catalogue) %>%
     	        group_by(publication_decade, language) %>%
                summarise(n = n(),
	               paper = sum(paper.consumption.km2, na.rm = TRUE))
